\addcontentsline{toc}{chapter}{Abstract}
\chapter*{Abstract}
\selectlanguage{english}
	Recent cationic technological advancements in the field of information and communication have introduced intelligent ways to manage various aspects of life.
	
	In this context, doing pattern recognition processing on videos in real time, the capabilities of statistical machine learning methods are limited by computing time rather than sample size. A more precise analysis reveals qualitatively different trade-offs for the case of small and large-scale learning problems. The large-scale case involves the computational complexity of the underlying optimization algorithm in a non-trivial way. Unlikely optimization algorithms such as stochastic gradient descent show amazing performance for large scale problems. In particular, the second order stochastic gradient and the averaged stochastic gradient are asymptotically efficient after a single pass over the training set.
	This work aims to provide an artificial intelligence (AI) -based intelligent system for vehicle license plate recognition using the Ridge Stochastic Gradient Descent Adaline (aka RASGD) Ridge Stochastic Gradient Descent Classifier.
	To minimize the cost function of the classifier, the RASGD adopts an unconstrained optimization model. In addition, to increase the speed of convergence of the classifier, the Adaline Stochastic Gradient Descent classifier is integrated with Ridge Regression.
	Finally, to validate the efficiency of intelligent system, the results of the proposed scheme were compared with advanced machine learning algorithms such as Support Vector Machine (SVM) and logistic regression methods. The intelligent RASGD system achieves 92\% accuracy, which is better than other selected classifiers.
	
	\vspace{2 cm}

\begin{singlespace}
\textbf {Keywords ~:} Suppevised Learning, Computer Vision, Stocastic Gradiant Descent, Objects recognition.
\end{singlespace}
\selectlanguage{french}